Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View

### 2020-07-14 Manuscript/sec3-experiment-design.tex
Add sketch of Section 4.

	\item[Q1] \emph{How do the hyper-parameters affect the training time and the memory usage of a GNN?}

@@

	\item[Q2] \emph{Which stage is the most time-consuming stage in GNN training?}

@@

	\item[Q3] \emph{Which consumes most of memory in GNN training?}

@@

	\item[Q4] \emph{Can the sampling techniques remove the performance bottleneck in GNN training?}

>>>>

	\item[Q1] \emph{How do the hyper-parameters affect the training time and the memory usage of a GNN?} (Section~\ref{sec:effects_of_hyper-parameters_on_performance})

@@

	\item[Q2] \emph{Which stage is the most time-consuming stage in GNN training?} (Section~\ref{sec:training_time_breakdown})

@@

	\item[Q3] \emph{Which consumes most of memory in GNN training?} (Section~\ref{sec:memory_usage_analysis})

@@

	\item[Q4] \emph{Can the sampling techniques remove the performance bottleneck in GNN training?} (Section~\ref{sec:effects_of_sampling_techniques_on_performance})

### 2020-07-14 Manuscript/sec4-experiments.tex
Add sketch of Section 4.

>>>>

In this section, we answers the four questions in Section~\ref{sec:experimental_scheme} one by one with experiments.

\subsection{Effects of Hyper-parameters on Performance}
\label{sec:effects_of_hyper-parameters_on_performance}

\subsection{Training Time Breakdown}
\label{sec:training_time_breakdown}

\subsection{Memory Usage Analysis}
\label{sec:memory_usage_analysis}

\subsection{Effects of Sampling Techniques on Performance}
\label{sec:effects_of_sampling_techniques_on_performance}
